This is an example of article title

### 2023-07-05 paper/paper.tex
chore: Paper additions PBMC MNIST

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/experiments/b_vs_d.png}
  }
  \caption{ Exponential decrease of mean number of points per leaf node }
  \label{b_vs_d}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/experiments/scale_n.png}
  }
  \caption{ Linear runtime scaling }
  \label{scale_n}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/experiments/scale_t.png}
  }
  \caption{ Parallelization scaling }
  \label{scale_t}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/uniform_2d/hist.png}
  }
  \caption{ Distribution of leaf node length }
  \label{uniform-2d-hist}
\end{figure}

@@

\subsection{Uniform data 10 dimensions}
\subsection{MNIST data 10 dimensions}
\subsection{PBMC data 10 dimensions}
\subsection{PBMC 36 dimensions}

>>>>

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/b_vs_d.png}
  }
  \caption{ Exponential decrease of mean number of points per leaf node }
  \label{b_vs_d}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/scale_n.png}
  }
  \caption{ Linear runtime scaling }
  \label{scale_n}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/scale_t.png}
  }
  \caption{ Parallelization scaling }
  \label{scale_t}
\end{figure}

@@

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/uniform_2d/hist.png}
  }
  \caption{ Distribution of leaf node length }
  \label{uniform-2d-hist}
\end{figure}

@@

\subsection{PBMC 30 dimensions}

The PBMC dataset exhibits outliers, which introduces challenges in the
normalization process. It causes the majority of data points to be clustered
into a single node for the first three levels of the tree. As depicted in
Figures \ref{pbmc-30-hist} (a), (b), and (c), the majority of points are
concentrated within a maximum of two nodes at these initial levels.
\\\\
However, the fourth and final level of the tree highlights the impact of the
dataset's high dimensionality. As indicated by Figure \ref{pbmc-30-hist} (d),
it becomes apparent that most points are now assigned to nodes with a length of
only $1$.

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/pbmc_30/hist_1.png}
    \includegraphics[width=10pc]{figures/experiments/pbmc_30/hist_2.png}
  }
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/pbmc_30/hist_3.png}
    \includegraphics[width=10pc]{figures/experiments/pbmc_30/hist_4.png}
  }

  \caption{
    30-Dimensional PBMC data distribution of leaf node length for tree level
    (a) 1 (b) 2 (c) 3 (d) 4.
  }
  \label{pbmc-30-hist}
\end{figure}

\subsection{MNIST 30 dimensions}

Unlike the PBMC dataset, the MNIST dataset does not exhibit significant
outliers. As a result, the distribution between the leaf nodes in the tree
becomes more uniform. Figure \ref{mnist-30-hist} (a) reveals that a majority of
points are concentrated within leaf nodes that possess sufficiently large
lengths. This favorable grouping indicates a more balanced distribution of data
points.
\\\\
However, as we progress to higher levels of the tree, the impact of the
dataset's high dimensionality becomes apparent. Consequently, the points become
exponentially sparser, leading to the formation of singleton leaf nodes.
This observation is clearly demonstrated in Figure \ref{mnist-30-hist} (b).

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/mnist_30/hist_1.png}
    \includegraphics[width=10pc]{figures/experiments/mnist_30/hist_2.png}
  }

  \caption{
    30-Dimensional MNIST data distribution of leaf node length for tree level
    (a) 1 (b) 2
  }
  \label{mnist-30-hist}
\end{figure}

Figure \ref{mnist-30-hist-th} indicates that adjusting the \verb|Small|
threshold to approximately $10000$ causes a shift in nodes from the region of
$\geq 10000$ to the histogram's small node region, while leaving the rest of
the nodes intact. This outcome is expected because nearly all points in the
$\geq 10000$ region are mapped to a singleton node in the subsequent recursion.

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=10pc]{figures/experiments/mnist_30/hist_3.png}
  }

  \caption{
    30-Dimensional MNIST data distribution of leaf node length for tree level
    2. Using Small threshold of 10000.
  }
  \label{mnist-30-hist-th}
\end{figure}
